Supplementary information

### 2019-12-15 manuscript/supplementary.Rmd
added table captions

phenotypic_descriptor_info %>%
  select(-`Descriptor Type`,-`Data Type`) %>%
  kable(format = 'latex',booktabs = TRUE,longtable = TRUE) %>%
  kable_styling(latex_options = c('striped','repeat_header'),repeat_header_continued = TRUE) %>%
  # column_spec(1,width = '1.5cm') %>%
  column_spec(1,width = '3cm') %>%
  column_spec(2:3,width = '6cm') #%>%
  # collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```

>>>>

phenotypic_descriptor_info %>%
  select(-`Descriptor Type`,-`Data Type`) %>%
  kable(format = 'latex',
        booktabs = TRUE,
        longtable = TRUE,
        caption = 'Phenotypic descriptors collected for oak decline severity.') %>%
  kable_styling(latex_options = c('striped','repeat_header'),repeat_header_continued = TRUE) %>%
  # column_spec(1,width = '1.5cm') %>%
  column_spec(1,width = '3cm') %>%
  column_spec(2:3,width = '6cm') #%>%
  # collapse_rows(columns = 1,latex_hline = "major", valign = "middle")
```
